CMPSubset

### 2021-08-16 CMP/CMPSubset.Rmd
continued clustree analysis

### Color palette
```{r}
color.palette <- c(
	"coral",
	"chartreuse4",
	"goldenrod1",
	"cadetblue1",
	"burlywood",
	"brown",
	"brown1",
	"blue",
	"blue4",
	"azure3",
	"aquamarine",
	"antiquewhite",
	"cadetblue",
	"gold3",
	"black",
	"darkgreen",
	"deeppink",
	"darkviolet",
	"darkturquoise",
	"darkslategray",
	"darksalmon",
	"darkorchid1",
	"darkolivegreen2",
	"forestgreen",
	"dodgerblue",
	"green",
	"lightpink",
	"lightcoral",
	"khaki1",
	"maroon",
	"peru",
	"lightseagreen",
	"lightsalmon",
	"plum",
	"moccasin",
	"tan",
	"tan1", 
	"red", 
	"purple",
	"khaki4",
	"black", 
	"plum4"
)
```

@@

@@

### Clustree
what's the max resolution we can achieve while keepign clusters stable?
```{r fig.width = 10, fig.height = 5}
clustree(cmp.object, prefix = "RNA_snn_res.", node_colour = "sc3_stability", exprs = "scale.data") + 
    scale_color_continuous(low = 'red3', high = 'white')
```
I think I'm liking res.1.0 from this

@@

# Total var 95%
## Neighborhood and umap
set total.var <- 95%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 95))

@@

>>>>

@@

```
Plot UMAP

```{r}
for(x in c(0.5, 1, 1.5, 2, 2.5)){
	cmp.object <- FindClusters(cmp.object, resolution = x)
}
saveRDS(cmp.object, file = paste0(projectName, "_dim", ndims, ".RDS"))
```

@@

### Clustree
what's the max resolution we can achieve while keepign clusters stable?
```{r fig.width = 10, fig.height = 5}
plot.title <- paste0(projectName, "_clustree_ndim", max(cmp.object@commands$RunUMAP.RNA.pca$dims))
my.clustree <- clustree(cmp.object, prefix = "RNA_snn_res.", node_colour = "sc3_stability", exprs = "scale.data") + 
	scale_color_continuous(low = 'red3', high = 'white') + 
	ggtitle(plot.title)
png(filename = paste0(plot.title, ".png"), height = 800, width = 1600)
plot(my.clustree)
dev.off()

```
I think I'm liking res.1.0 from this. Although how much does this change if I use fewer PCs...

@@

# Total var 85%
## Neighborhood and umap
set total.var <- 85%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 85))

@@

### Clustree
what's the max resolution we can achieve while keepign clusters stable?
```{r fig.width = 10, fig.height = 5}
plot.title <- paste0(projectName, "_clustree_ndim", max(cmp.object@commands$RunUMAP.RNA.pca$dims))
my.clustree <- clustree(cmp.object, prefix = "RNA_snn_res.", node_colour = "sc3_stability", exprs = "scale.data") + 
	scale_color_continuous(low = 'red3', high = 'white') + 
	ggtitle(plot.title)
png(filename = paste0(plot.title, ".png"), height = 800, width = 1600)
plot(my.clustree)
dev.off()
```

# Total var 95%

## Neighborhood and umap
set total.var <- 95%
```{r}
tot.var <- percent.variance(cmp.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 95))

```{r}
cmp.object <- readRDS("CMP_dim41.RDS")
```

```{r fig.width = 10, fig.height = 5}
plot.title <- paste0(projectName, "_clustree_ndim", max(cmp.object@commands$RunUMAP.RNA.pca$dims))
my.clustree <- clustree(cmp.object, prefix = "RNA_snn_res.", node_colour = "sc3_stability", exprs = "scale.data") + 
	scale_color_continuous(low = 'red3', high = 'white') + 
	ggtitle(plot.title)
png(filename = paste0(plot.title, ".png"), height = 800, width = 1600)
plot(my.clustree)
dev.off()
```
